---
title: "Introduction to TreeBreaker as a R package"
author: "Xavier Didelot"
date: "`r Sys.Date()`"
vignette: |
  %\VignetteEngine{knitr::rmarkdown}  %\VignetteIndexEntry{Introduction to TreeBreaker as a R package}    %\usepackage[utf8]{inputenc}
output: html_document
---

## About this page...

This page describes the use of TreeBreaker as a R package. If you would prefer to use TreeBreaker as a standalone application, see [here](https://github.com/ansariazim/treeBreaker). 

## Installation

```{r "setup", include=FALSE}
require("knitr")
opts_knit$set(root.dir = "..")
```

The package can be installed in R using the command:
```{r, eval=FALSE}
devtools::install_github('ansariazim/treeBreaker')
```

You should then be able to load the package with:
```{r}
library(treeBreaker)
```

## Analysis

Analysis can be performed using the command:
```{r}
res=treeBreaker('testData/testTree.newick','testData/phenoTestFile.txt','out')
```

The first argument is the name of a Newick file containing the tree to analyse, the second argument is the name of a tab separated file containing the phenotype data, and the third argument is the name of a file in which to store the results.

```{r, include = F}
file.remove('out')
```

## Exploring the results

Once the analysis has finished running, results can be displayed as follows:

```{r}
plot(res)
```

```{r}
plot(res,'trace')
```

```{r}
plot(res,'states')
```

```{r}
plot(res,'correlation')
```

